%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\usepackage[utf8]{inputenc}
\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
%\usepackage{fontspec}

\usepackage[scale=0.75]{geometry} % Reduce document margins
\setlength{\hintscolumnwidth}{4cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Pablo} % Your first name
\familyname{Riutort Grande} % Your last name



%----------------------------------------------------------------------------------------

\begin{document}



%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	INFO SECTION
%----------------------------------------------------------------------------------------

\section{Contact}

\cvitem{Phone}{+34 693 948 133}
\cvitem{Email}{pablo.riutort@gmail.com}
\cvitem{Web}{\href{https://github.com/pablorgr}{github.com/pablorgr}}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{Currently}{Inter-University Master's Degree in Computational Engineering and Mathematics}{}{joint Open University of Catalonia and Rovira and Virgili University}{}{}
\cventry{}{Information and Communication Technology Security Master's Degree (MISTIC)}{}{joint Open University of Catalonia, Autonomous University of Barcelona, Rovira and Virgili University}{}{
Thesis in Protocols and security applications:
\begin{itemize}
\item Developing article: \textit{How p2p framework can help mitigate trust and
security risks of IoT applications
A .onion based framework to address trust and privacy issues for
the IoT.}
\item Working in an IoT framework with emphasis in privacy using Tor and .onion services
\end{itemize}
}
\cventry{}{Computer Engineering Degree}{mention in Information Technology}{University of the Balearic Islands}{}{Final project: STFile - Python wrapper for RDFLib applied to a file system ontology. Semantics applied to a *NIX file system.}
\cventry{}{EUROWEB+ scholarship}{Computer Science and Informatics}{Faculty of Electronic Engineering}{Univerity of Nis}{} % Arguments not required can be left empty


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\cventry{2021}{Specialist SW Network as a Platform}{\textsc{Vodafone}}{Madrid}{}{
\begin{itemize}
\item Backend development with Flask and Kubernetes.
\item Innovation projects with MQTT, Python and JavaScript.
\item Project maintenance with Python and Bash
\end{itemize}
}
\cventry{2019-2021}{Python Developer}{\textsc{Qvantel}}{Madrid}{}{
\begin{itemize}
\item Backend development with Django, mariadb, docker-compose and RabbitMQ.
\item Taylored solutions development with Python, Bottle, jQuery and robot framework.
\item KPIs and automation.
\item TDD and good practices introduction into development cycle.
\item Core maintenance with Python and bash.
\end{itemize}
}
\cventry{2018--2019}{Python Developer}{\textsc{SMACH Team}}{Palma de Mallorca - Parc Bit}{}{App and backend development}

\cventry{2017--2018}{Software Engineer}{\textsc{SmartUIB}}{University of the  Balearic Islands}{}{Creation and development of projects framed into Smart Cities, energy efficiency and IoT.
\begin{itemize}
\item Web Services SOAP with OCPP protocol.
\item Sensors and other services integrations with Python for Sentilo system.
\item Elasticsearch and Kibana for data visualization.
\item API development and dashboard for IoT device control.
\end{itemize}
}

\cventry{2014--2016}{Lead developer}{\textsc{Civitfun}}{Palma de Mallorca - Parc Bit}{}{Web development of \href{http://civitfun.com/en/}{civitfun.com} focusing in backend, integrations, maintenance and design of databases.}

\cventry{2013--2014}{Web developer}{\textsc{Mola}}{Palma de Mallorca - Parc Bit}{Talentum Startups internship}{Started as a web developer thanks to an intership in a startup incubator were I worked in backend maintenance and project design.}


\section{Metions \& Awards}
\cventry{2013}{Talentum Startups internship}{\textsc{Telefonica}}{}{}{
Talentum Startups is an intership for students allowing them to enjoy an enterpreneur experience along with the opportunity to improve society from a technologic perspective.}

%------------------------------------------------
%	SKILLZ
%----------------------------------------------------------------------------------------

\section{Skills}
\cvitem{Programming}{Python, JavaScript, Bash, PHP, Java}
\cvitem{Databases}{mariadb, MySQL, sqlite, MongoDB}
\cvitem{Frameworks}{Django, Flask, Bottle, jQuery, Laravel}
\cvitem{Frontend}{HTML/CSS, Bootstrap, QML}
\cvitem{}{Git, Linux, Docker, docker-compose, REST, JSON, RabbitMQ, XML, SOAP, MQTT, Kafka}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitem{Spanish}{Native}
\cvitem{Catalan}{Fluent}
\cvitem{English}{Fluent}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Hobbies}
\cvitem{}{Science and technology}{}
\cvitem{}{Cinema and TV Shows}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Other}
\cvitem{}{Willing to relocate and travel for business}
\cvitem{}{Driving license}



%----------------------------------------------------------------------------------------

\end{document}
